\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-01-30 trunk/related.tex
updates

\begin{wrapfigure}{r}{0.2\textwidth}
 \centering
 \includegraphics[scale=0.3]{figs/planner-arch.pdf}
 \caption{\small A general architectural block diagram for an
   Artificial Intelligence based Planner.}
 \label{fig:planner}
\end{wrapfigure}

@@

Our system, \texttt{T-REX}, the focus of this chapter, is an agent
control structure formally defined as a composition of coordinated
control loops with a recurring sense-plan-act (SPA)
cycle. \texttt{T-REX} was designed after carefully evaluating lessons
learned from the IDEA and owes substantially to the notion of
partitioned problem solving from that effort. However this
partitioning is systematic and methodologically principled where we
manage the information flow within the partitioned structure to ensure
consistency in order to direct the flow of goals and observations in a
timely manner. The resulting control structure improves scalability
since many details of each controller can be encapsulated within a
single control loop.  Furthermore, partitioning increases robustness
since controller failure can be localized to enable graceful system
degradation, making this an effective \emph{divide-and-conquer}
approach to the overall control problem.

>>>>

\begin{figure}[htpb]
 \centering
 \includegraphics[scale=0.3]{figs/planner-arch.pdf}
 \caption{\small A general architectural block diagram for an
   Artificial Intelligence based Planner.}
 \label{fig:planner}
\end{figure}

@@

Our system, \texttt{T-REX}, the focus of this chapter, is an agent
control structure formally defined as a composition of coordinated
control loops with a recurring sense-plan-act (SPA)
cycle. \texttt{T-REX} was designed after carefully evaluating lessons
learned from \texttt{IDEA} and owes substantially to the notion of
partitioned problem solving from that effort. However this
partitioning is systematic and methodologically principled where we
manage the information flow within the partitioned structure to ensure
consistency in order to direct the flow of goals and observations in a
timely manner. The resulting control structure improves scalability
since many details of each controller can be encapsulated within a
single control loop.  Furthermore, partitioning increases robustness
since controller failure can be localized to enable graceful system
degradation, making this an effective \emph{divide-and-conquer}
approach to the overall control problem.
